Low Dimensional Embedding of Climate Data for Radio Astronomical Site Testing in the Colombian Andes

### 2017-05-09 pasp/paperclimate.tex
penultimos cambios de oleonardo

\begin{table}
\caption{\label{tabfin}Regions of interest with a high-altitude daytime dry, clear-sky climate, organized by geographical cluster number ($N_C$), station location, Bayesian probability quality measure ($Q_j$), distance to cluster center ($r_c$), mean precipitation  ($\bar{R}$), mean rain days ($\bar{D}$), mean relative humidity  ($\bar{H}$), mean sunshine duration  ($\bar{S}$), and altitude ($h$). Detailed table (including all clusters) available at \texttt{https://github.com/saint-germain/ideam} \\}
%https://tex.stackexchange.com/questions/98388/how-to-make-table-with-rotated-table-headers-in-latex

\begin{tabular}{rlrrrrrrr}

@@

 $N_C$  &                 Municipality  &  $Q_j$ &  $r_c$  &   $\bar{R}$ &   $\bar{D}$  &   $\bar{H}$  &  $\bar{S}$ &  $h$ \\

@@

              2 &                      Nemocon &            2.2 &                        28 &                        66 &                   ND &                        ND &                          ND &    2600 \\
              2 &                         Susa &            4.6 &                        18 &                        83 &                   12 &                        ND &                          ND &    2600 \\
              2 &                     Cucunuba &            4.7 &                         6 &                        57 &                    9 &                        ND &                          ND &    2620 \\
              2 &                    Sutatausa &            4.8 &                         6 &                        57 &                   10 &                        ND &                          ND &    2700 \\
              2 &                     Guacheta &            4.9 &                        16 &                        73 &                   10 &                        ND &                          ND &    2690 \\
              2 &                  Lenguazaque &            5.2 &                        10 &                        63 &                   12 &                        ND &                          ND &    2650 \\
              2 &                     Simijaca &            5.2 &                        23 &                        67 &                   11 &                        ND &                          ND &    2572 \\
              2 &                       Suesca &            5.6 &                        20 &                        59 &                   10 &                        ND &                          ND &    2575 \\
              2 &             Carmen de Carupa &            6.1 &                        12 &                        54 &                   12 &                        ND &                          ND &    2970 \\
              2 &                     Cucunuba &            6.1 &                         7 &                        51 &                    5 &                        ND &                          ND &    2562 \\
              2 &                  Lenguazaque &            6.1 &                         9 &                        57 &                   10 &                        ND &                          ND &    2585 \\
              2 &                         Susa &            6.1 &                        11 &                        60 &                    8 &                        ND &                          ND &    3130 \\
              2 &  Ubate &            6.1 &                         4 &                        62 &                   13 &                        ND &                          ND &    2555 \\
              2 &  Ubate &            6.1 &                         5 &                        62 &                   12 &                        ND &                          ND &    2610 \\
              2 &                      Nemocon &            7.6 &                        20 &                        52 &                   10 &                        77 &                           4 &    2580 \\

@@

              4 &                      Duitama &            4.0 &                        17 &                        69 &                   10 &                        ND &                          ND &    2590 \\
              4 &                        Paipa &            4.0 &                        12 &                        74 &                    9 &                        ND &                          ND &    2900 \\
              4 &                        Nobsa &            5.0 &                         6 &                        66 &                   10 &                        ND &                          ND &    2500 \\
              4 &        Santa Rosa &            5.0 &                        10 &                        70 &                    9 &                        ND &                          ND &    2500 \\
              4 &                     Sogamoso &            5.0 &                         4 &                        59 &                   10 &                        ND &                          ND &    2500 \\
              4 &                     Sogamoso &            5.0 &                         7 &                        60 &                   12 &                        ND &                          ND &    2500 \\
              4 &                     Tibasosa &            5.0 &                         5 &                        62 &                    7 &                        ND &                          ND &    2500 \\
              4 &                          Iza &            5.6 &                        12 &                        52 &                    9 &                        ND &                          ND &    2470 \\
              4 &                   Firavitoba &            6.1 &                         6 &                        57 &                    9 &                        ND &                          ND &    2486 \\
              4 &                       Mongui &            6.1 &                        12 &                        65 &                    9 &                        ND &                          ND &    2970 \\
              4 &                     Sogamoso &            6.1 &                        11 &                        65 &                   10 &                        ND &                          ND &    3225 \\
              4 &                     Sogamoso &            6.7 &                         5 &                        61 &                   12 &                        75 &                           5 &    2500 \\
              4 &                        Nobsa &           10.0 &                        10 &                        68 &                   13 &                        74 &                           4 &    2530 \\

>>>>

\begin{table}
\caption{\label{tabfin}Stations in two regions of interest (RI) showing a high-altitude daytime dry, clear-sky climate, organized by location, Bayesian probability quality measure ($Q_j$), distance to cluster center ($r_c$), mean precipitation  ($\bar{R}$), mean rain days ($\bar{D}$), mean relative humidity  ($\bar{H}$), mean sunshine duration  ($\bar{S}$), and altitude ($h$). Detailed table (including all clusters) available at \texttt{https://github.com/saint-germain/ideam} \\}
%https://tex.stackexchange.com/questions/98388/how-to-make-table-with-rotated-table-headers-in-latex

\begin{tabular}{clrrrrrrr}

@@

RI&                   Municipality  &  $Q_j$ &  $r_c$  &   $\bar{R}$ &   $\bar{D}$  &   $\bar{H}$  &  $\bar{S}$ &  $h$ \\

@@

            &                       Nemocon &            2.2 &                        28 &                        66 &                   ND &                        ND &                          ND &    2600 \\
            &                          Susa &            4.6 &                        18 &                        83 &                   12 &                        ND &                          ND &    2600 \\
            &                      Cucunuba &            4.7 &                         6 &                        57 &                    9 &                        ND &                          ND &    2620 \\
            &                     Sutatausa &            4.8 &                         6 &                        57 &                   10 &                        ND &                          ND &    2700 \\
            &                      Guacheta &            4.9 &                        16 &                        73 &                   10 &                        ND &                          ND &    2690 \\
            &                   Lenguazaque &            5.2 &                        10 &                        63 &                   12 &                        ND &                          ND &    2650 \\
            &                      Simijaca &            5.2 &                        23 &                        67 &                   11 &                        ND &                          ND &    2572 \\
            &                        Suesca &            5.6 &                        20 &                        59 &                   10 &                        ND &                          ND &    2575 \\
                      \rotatebox{90}{\rlap{Valle de Ubat\'e}}
            &              Carmen de Carupa &            6.1 &                        12 &                        54 &                   12 &                        ND &                          ND &    2970 \\
            &                      Cucunuba &            6.1 &                         7 &                        51 &                    5 &                        ND &                          ND &    2562 \\
            &                   Lenguazaque &            6.1 &                         9 &                        57 &                   10 &                        ND &                          ND &    2585 \\
            &                          Susa &            6.1 &                        11 &                        60 &                    8 &                        ND &                          ND &    3130 \\
            &   Ubate &            6.1 &                         4 &                        62 &                   13 &                        ND &                          ND &    2555 \\
            &   Ubate &            6.1 &                         5 &                        62 &                   12 &                        ND &                          ND &    2610 \\
            &                       Nemocon &            7.6 &                        20 &                        52 &                   10 &                        77 &                           4 &    2580 \\

@@

            &                       Duitama &            4.0 &                        17 &                        69 &                   10 &                        ND &                          ND &    2590 \\
            &                         Paipa &            4.0 &                        12 &                        74 &                    9 &                        ND &                          ND &    2900 \\
            &                         Nobsa &            5.0 &                         6 &                        66 &                   10 &                        ND &                          ND &    2500 \\
            &         Santa Rosa &            5.0 &                        10 &                        70 &                    9 &                        ND &                          ND &    2500 \\
            &                      Sogamoso &            5.0 &                         4 &                        59 &                   10 &                        ND &                          ND &    2500 \\
            &                      Sogamoso &            5.0 &                         7 &                        60 &                   12 &                        ND &                          ND &    2500 \\
            &                      Tibasosa &            5.0 &                         5 &                        62 &                    7 &                        ND &                          ND &    2500 \\
                                              \rotatebox{90}{\rlap{~Valle del Sol}}
            &                           Iza &            5.6 &                        12 &                        52 &                    9 &                        ND &                          ND &    2470 \\
            &                    Firavitoba &            6.1 &                         6 &                        57 &                    9 &                        ND &                          ND &    2486 \\
            &                        Mongui &            6.1 &                        12 &                        65 &                    9 &                        ND &                          ND &    2970 \\
            &                      Sogamoso &            6.1 &                        11 &                        65 &                   10 &                        ND &                          ND &    3225 \\
            &                      Sogamoso &            6.7 &                         5 &                        61 &                   12 &                        75 &                           5 &    2500 \\
            &                         Nobsa &           10.0 &                        10 &                        68 &                   13 &                        74 &                           4 &    2530 \\
